---
title: "Simple document"
author: "Mingyin Wang"
output: html_document
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

## learning assessment
## I loaded necessary packages(ex. tidyverse)

it creates "la_df"

```{r}
library(tidyverse)
la.df=
  tibble(
    norm_samp=rnorm(n=500, mean=1),
    samp_geq0=norm_samp>0,
    abs_v_samp=abs(norm_samp)
  )
ggplot(la.df, aes(x=abs_v_samp)) + 
  geom_histogram()

```

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell